Current State of Knowledge Representation Systems for Robotics

### 2011-11-22 krs-survey.tex
Added some 'desirable features' for KRS from MCCarthy
While here, renamed paper.tex into krs-survey.tex

\paragraph{General views on what is missing to AI} \cite{McCarthy2007}

\paragraph{Natural language processing in situated context}
In~\cite{Roy2005}, Roy and Reiter summarize what they see as the main
challenges to be tackled: cross-modal representation systems, association of
words with perceptual and action categories, modeling of context, figuring out
the right granularity of models, integrating temporal modeling and planning,
ability to match past (learned) experiences with the current interaction and
ability to take into account the human perspective.

@@

>>>>

Several authors from fields that are connex to the robotics have previously listed desirable features of systems aiming at cognitive abilities as rich as possible.

\paragraph{McCarthy: Towards human-level AI}

In~\cite{McCarthy2007}, McCarthy lists the challenges he identifies on the road
to a \emph{human-level AI}.

	\item the ability to \emph{"operate successfully in the common sense
	informatic situation"},

	\item the necessity of relying on mathematical logic, as the most fruitful
	formalism for machine intelligence,

	\item the ability to deal with \emph{approximate concepts and approximate
	theories} (that would include representing them, and reasoning with them),

	\item nonmonotonic reasoning \fxfatal{give here a clear example},

	\item what McCarthy calls \emph{Elaboration Tolerance}, \ie, the ability to
	extend \emph{on requirement} the closed domain of interpretation for a
	given assertion,

	\item the ability to formalize and reason about contexts,

	\item reasoning about events, and in particular, actions,

	\item the capacity of introspection,

	\item and finally, he points the issue of giving computer the right
	heuristics for decision making.

Knowledge representation systems are concerned by most, if not all, of this
points.

\paragraph{Natural language processing in situated context}

In~\cite{Roy2005}, Roy and Reiter summarize what they see as the main
challenges to be tackled: cross-modal representation systems, association of
words with perceptual and action categories, modeling of context, figuring out
the right granularity of models, integrating temporal modeling and planning,
ability to match past (learned) experiences with the current interaction and
ability to take into account the human perspective.

@@

On modal logics, see the remark of McCarthy, in \cite{McCarthy2007}, section 3
